### 2021-11-03 publication/conclusion.tex
Editing
Fix citet

The Feature-First Block Model (FFBM) introduced 
in this paper is a new generative model for labelled networks,
developed to address difficulties of other graphical models 
when testing how vertex features affect community structure. The idea 
is to divide the graph into its most natural partition and determine whether 
the vertex features can accurately explain this partition. 
It is relatively easy to find vertex features that are in some way 
correlated with the graphical structure. Nonetheless, only when 
we find the feature that best describes the most pronounced partition 
do we have a stronger case for causation.

Using this new model,
we go on to describe an efficient inference algorithm to sample 
the parameters of the FFBM. 
This takes the form of a two-level Markov chain,
used to sample the block memberships $b$ and block generator 
parameters $\theta$. These chains can either be executed
in parallel or 
the empirical mean of the $b$-samples can be used
as the input to the $\theta$-chain. The latter option
reduces the variance in our evaluation of the target distribution 
and thus shortens burn-in.

The overall method is shown to be effective at extracting and describing 
the most natural communities in a labelled network. Nevertheless, the approach 
can only currently explain the structure at the macro-scale. We cannot 
explain structure within each block. Future work will benefit from extending 
the FFBM to be hierarchical in nature. That way, the structure of the network 
can be explained at all length-scales of interest. So long as data 
collection techniques remain ethical and care is taken to respect 
personal privacy, such empowered decision-making can only help humankind.

>>>>

The Feature-First Block Model (FFBM) introduced 
in this paper is a new generative model for labelled networks well-suited for describing how features
affect structure. The idea is to divide the graph into its most natural partition and determine whether 
the vertex features can accurately explain this partition. 
It is easy to find vertex features that are in some way 
correlated with the graphical structure; only when 
we find the feature that best describes the most pronounced partition,
do we have a stronger case for causation.

Using this new model,
we go on to describe an efficient inference algorithm to sample 
the parameters of the FFBM. 
This is shown to be effective at extracting and describing 
the most natural communities in a labelled network. Nevertheless, the approach 
can only currently explain the structure at the macro-scale. Future work will benefit from extending 
the FFBM to be hierarchical in nature. That way, the structure of the network 
can be explained at all length-scales of interest.

### 2021-11-03 publication/extensions.tex
Fix citet

The greatest limitation of the current FFBM formulation is that it can only explain structure at the macro-scale. In other words, we cannot explain structure within each detected block. Future work will benefit from extending the FFBM to be hierarchical in nature. This would be a relatively natural extension. Indeed, the SBM has already been extended to a hierarchical form, often called the nested SBM \cite{SBM-hierarchical}. The idea is to divide each block into sub-blocks and so on recursively until a specified depth is reached. The full block membership for a particular vertex now encodes the memberships at all levels of the hierarchy.

The necessary modification of the feature-to-block generator is also rather natural. Given the nested SBM, we would have a hierarchy of generators, each generating a block membership at a particular level of the hierarchy. Nevertheless, this does pose some practical issues for scalability; supposing we have $L$ levels in our hierarchy and each divides the parent block into $B$ sub-blocks, then the number of distinct generators necessary scales as $O(B^L)$. To avoid exponential growth in the number of model parameters, we could apply some form of dimensionality reduction as we descend the layers so that each generator is only given relevant features as input.

>>>>

The current FFBM formulation can only explain macro-structure and not structure within each detected block. Future work will benefit from extending the FFBM to be hierarchical in nature. Indeed, the SBM has already been extended to a hierarchical form, often called the nested SBM \cite{SBM-hierarchical}.

The necessary modification of the feature-to-block generator is also rather natural. Given the nested SBM, we would have a hierarchy of generators, each generating a block membership at a particular level of the hierarchy. To avoid exponential growth in the number of model parameters, we could apply some form of dimensionality reduction as we descend the layers so that each generator is only given relevant features as input.

### 2021-11-03 publication/ffbm.tex
Brevify polbooks
Fix citet

In this section we propose a novel generative model for labelled networks. We call this the feature-first block model (FFBM -- illustrated in figure~\ref{fig:ffbm}).

@@

\citet{Peixoto-Bayesian-Microcanonical} proposes careful choices for 
the priors on the additional microcanonical SBM parameters $\psi$, which we adopt. 
The idea is to write the joint distribution on $(b, e, k)$ as a product of 
conditionals, $p(b, e, k) = p(b) p(e | b) p(k | e, b)= p(b) p(\psi | b)$. 
In our case, conditioning on $X$ is also necessary, leading to,
%
\begin{equation}
	p(b, \psi | X) = p(b | X) p(\psi | b, X) = p(b | X) p(\psi | b),
	\label{eqn:joint-pseudo-prior}
\end{equation}
%
where we used the fact $\psi$ and $X$ are conditionally 
independent given $b$.
All that concerns the main argument is that it has
an easily computable form.

>>>>

In this section we propose a novel generative model for labelled networks. We call this the feature-first block model (FFBM -- illustrated in Figure~\ref{fig:ffbm}).

@@

Peixoto \cite{Peixoto-Bayesian-Microcanonical} proposes careful choices for 
the priors on the additional microcanonical SBM parameters $\psi$, which we adopt. 
The idea is to write the joint distribution on $(b, e, k)$ as a product of 
conditionals, $p(b, e, k) = p(b) p(e | b) p(k | e, b)= p(b) p(\psi | b)$. 
In our case, conditioning on $X$ is also necessary, leading to,
%
\begin{equation}
	p(b, \psi | X) = p(b | X) p(\psi | b, X) = p(b | X) p(\psi | b),
	\label{eqn:joint-pseudo-prior}
\end{equation}
%
where we used the fact $\psi$ and $X$ are conditionally 
independent given $b$.
All that concerns the main argument is that it has
an easily computable form.
